Polyester RNA-seq simulation study

### 2018-10-09 datasets/RNA-Seq/polyester-simulation.Rmd
Add ROC curves to yeast & polyester

plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

plotsim_average(res10d, met="rejections",filter_set = excludeSet, 
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

>>>>

plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met=c("FPR", "TPR"), filter_set = excludeSet,
                merge_ihw = TRUE)

@@

plotsim_average(res10d, met="rejections",filter_set = excludeSet, 
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met=c("FPR", "TPR"), filter_set = excludeSet,
                merge_ihw = TRUE)
